---
title: "Bitcoin Trading Indicators"
output: html_notebook
---

Create Bitcoin indicators for trading.


Set options and load packages
```{r}
options(scipen = 999, digits = 2)

library(tidyverse)
library(tseries)
library(tidyquant)
```



Using Quantmod

```{r}
getSymbols("BTC-USD")
BTC <- na.omit(`BTC-USD`)

getSymbols("ETH-USD")
ETH <- na.omit(`ETH-USD`)

getSymbols("T")
getSymbols("DKNG")
getSymbols("HAS")
getSymbols("NNDM")
getSymbols("BNGO")
getSymbols("PLTR")
getSymbols("ED")
getSymbols("O")
getSymbols("DVN")
getSymbols("VTIP")
getSymbols("BSV")

getSymbols("MAIN")
getSymbols("SRC")
```


Run the following code in the console:


chartSeries(SRC, TA = NULL,
            subset='last 18 months',
            theme=chartTheme('white')
            )
addEMA(n=3,on=1,col = "blue")
addEMA(n=15,on=1,col = "red")
addBBands(n=30,sd=2)
addMACD(fast=12,slow=26,signal=9,type="EMA")




Notes: 01/27/22
Crypto:
BTC - wait another week or two
ETH - wait another week or two

Cash equivalents:
BSV - hold
VTIP - hold

Income:
T - hold
HAS - watch. Could be a buy soon
ED - hold
O - hold
DVN - hold

Speculation
DKNG - Watch
NNDM - hold
BNGO - hold
PLTR - hold


Recommendations: 
No obvious buys at this time. Looking for good entry points into BTC, ETH, DKNG and HAS.






Calculate the likelihood of stock rising 10% or more in a 7, 14 and 30 day window based on previous 18 months of daily price history.
```{r}
stock <- tq_get("lumn", get = "stock.prices") 

stock <- stock %>%
  mutate(lag7 = lag(x = stock$adjusted, n = 7),
         lag14 = lag(x = stock$adjusted, n = 14),
         lag30 = lag(x = stock$adjusted, n = 30),
         ror7 = (adjusted - lag7)/lag7 * 100,
         ror14 = (adjusted - lag14)/lag14 * 100,
         ror30 = (adjusted - lag30)/lag30 * 100) %>%
  filter(date >= "2020-07-20")


   

mean7 <- mean(stock$ror7)
sd7 = sd(stock$ror7)
mean14 = mean(stock$ror14)
sd14 = sd(stock$ror14)
mean30 = mean(stock$ror30)
sd30 = sd(stock$ror30)
 
seven <- tibble(x = rnorm(n = 1000000, mean = mean7, sd = sd7))
fourteen <- tibble(x = rnorm(n = 1000000, mean = mean14, sd = sd14))
thirty <- tibble(x = rnorm(n = 1000000, mean = mean30, sd = sd30))

seven <- seven %>%
  mutate(over = if_else(x >= 10, 1, 0))

fourteen <- fourteen %>%
  mutate(over = if_else(x >= 10, 1, 0))

thirty <- thirty %>%
  mutate(over = if_else(x >= 10, 1, 0))

over_pct7 = sum(seven$over)/1000000
over_pct14 = sum(fourteen$over)/1000000
over_pct30 = sum(thirty$over)/1000000
        
```



