---
title: "Bitcoin Trading Indicators"
output: html_notebook
---

Create Bitcoin indicators for trading.


Set options and load packages
```{r}
options(scipen = 999, digits = 4)

library(tidyverse)
library(tseries)
library(quantmod)
```



Using Quantmod

```{r}
getSymbols("BTC-USD")
BTC <- na.omit(`BTC-USD`)

getSymbols("ETH-USD")
ETH <- na.omit(`ETH-USD`)

getSymbols("T")
getSymbols("DKNG")
getSymbols("HAS")
getSymbols("NNDM")
getSymbols("BNGO")
getSymbols("PLTR")
getSymbols("ED")

```


Run the following code in the console:

stock <- ED


chartSeries(stock,
            subset='last 18 months',
            theme=chartTheme('white')
            )
addEMA(n=3,on=1,col = "blue")
addEMA(n=15,on=1,col = "red")
addBBands(n=30,sd=2)
addMACD(fast=12,slow=26,signal=9,type="EMA")




Notes: 12/14/21
BTC - possible buy
ETH - not yet
T - oversold; possible buy
DKNG - oversold; possible buy
HAS - seems fairly priced but at recent highs
NNDM/BNGO - speculation plays; do not add more
PLTR - approaching oversold
ED - overbought?

Recommendations: Keep an eye on BTC for buying opportunity. Increase investment
in HAS if looking for quality dividends. Consider T and DKNG if looking to add
to position to lower cost basis.



Notes: 11/24/21
T is oversold
BTC/ETH not yet
DKNG is oversold
HAS approaching overbought
NNDM approaching oversold
BNGO seems fairly priced
PLTR fairly priced
ED approaching overbought






